### 2020-01-22 report/05-stability.Rmd
Cleaning report

```{r, fig.dim = c(10, 7), include = FALSE}
synchrony %>%
  left_join(select(temporal_community_metrics, station, richness_med), by =
    "station") %>%
  gather(comp, stab, synchrony:cv_com) %>%
  ggplot(aes(x = richness_med, y = stab)) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Species diversity", y = "Stability component") +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  facet_grid(rows = vars(comp), scales = "free_y")
```

@@

### Some temporal series of biomass

#### Total biomass

```{r, fig.dim = c(10, 7)}
community_metrics %<>% left_join(select(op_analysis, opcod, station, date))
station_high_low_stab <- temporal_community_metrics %>%
  arrange(desc(biomass_stab)) %>%
  slice(c(1:5, (n() - 4):(n() - 0))) %>%
  select(station) %>%
  unlist
names(station_high_low_stab) <- rep(c("high", "low"), each = 5) 
```

```{r tmp-stab, fig.dim = c(10, 7), fig.cap = "The five lowest and highest biomass stability"}
temporal_biomass <- community_metrics %>%
  filter(station %in% station_high_low_stab) %>%
  mutate(stab_status = ifelse(
      station %in% station_high_low_stab[names(station_high_low_stab) == "low"],
      "low", "high")) %>%
  group_by(stab_status, station) %>%
  nest() %>%
  group_by(stab_status) %>%
  mutate(id_stab = seq_along(station)) %>%
  unnest()
ggplot(temporal_biomass, aes(y = biomass, x = date)) +
  geom_line() +
  geom_point() +
  facet_grid(id_stab ~ stab_status, scales = "free_y") +
  labs(y = "Biomass (g)", x = "Date")
```

```{r more-stab-troph, fig.dim = c(10, 21), fig.cap = "The four station with the highest biomass stability. Dashed and solid lines represent respectively trophic species in the group 2 and 3."}

# Get biomass by sp node:
net_sp_troph <- select(network_analysis, opcod, composition) %>%
  unnest(composition)
# Get synchrony and cv sp:
sync_sp_troph <- get_sync_cv_mat(com_analysis = net_sp_troph, op_analysis = op_analysis)
# Get trophic lvl by node
trophic_level %<>%
  rename(species = sp_class) %>%
  mutate(troph_group = get_size_class(trophic_level, NULL, troph_level,
      trophic_class))

plot_stab <- purrr::map(station_high_low_stab, function (x) {
  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = TRUE)
  p + theme(legend.position="none") 
})
plot_grid(plotlist = plot_stab, ncol = 2)
```

```{r less-stab-troph, eval = FALSE, fig.dim = c(10, 7), fig.cap = "The four station with the lowest biomass stability. See caption of Figure for details."}
plot_grid(plotlist = plot_stab[7:10], ncol = 2)
```

```{r mid-stab-troph, eval = FALSE, fig.dim = c(10, 7), fig.cap = "Four stations with medium biomass stability. See caption of Figure for details."}
# Middle station 
plot_stab <- purrr::map(sync_sp_troph$station[209:212], function (x) {
  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = TRUE)
  p + theme(legend.position="none") 
})
plot_grid(plotlist = plot_stab[1:4], ncol = 2)
```

```{r 75-stab-troph, eval = FALSE, fig.dim = c(10, 7), fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
# Third quater
plot_stab <- purrr::map(sync_sp_troph$station[300:304], function (x) {
  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = FALSE)
  p + theme(legend.position="none") 
})
plot_grid(plotlist = plot_stab[1:4], ncol = 2)
```

```{r 25-stab-troph, eval = FALSE, fig.cap = "Four stations with medium/low biomass stability. See caption of Figure for details."}
# Third quater
plot_stab <- purrr::map(sync_sp_troph$station[104:107], function (x) {
  p <- plot_dyn_sp_biomass(sync = sync_sp_troph, trophic_level = trophic_level, station = x, .log = FALSE)
  p + theme(legend.position="none") 
})
plot_grid(plotlist = plot_stab[1:10], ncol = 2)
```

@@

```{r}
library(ade4)
library(factoextra)
myload(habitat_pressure, dir = mypath("report"))
```

@@

hab_press_div <- left_join(habitat_pressure,
  temporal_community_metrics[, c("station", "richness_med", "biomass_avg","biomass_stab")],
  by = "station") %>%
left_join(div_troph_grp, by = "station")
pca_hab <- dudi.pca(as.data.frame(select(na.omit(hab_press_div), -station)), scannf = FALSE, nf = 3, center = TRUE, scale = TRUE)

eig_plot <- fviz_eig(pca_hab)
pca_plot <- fviz_pca_var(pca_hab,
    axes = c(1, 2),
    col.var = "contrib", # Color by contributions to the PC
    gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
    repel = TRUE     # Avoid text overlapping
  )

ggdraw(pca_plot) + 
  draw_plot(eig_plot, x = .9, y = .95, hjust = 1, vjust = 1, width = 0.17, height = 0.25)
```

```{r}
m <- cor(as.matrix(select(na.omit(hab_press_div), -station)), method =
  "spearman")
corrplot::corrplot(m, order="hclust")
```

```{r, eval = FALSE}
mod <- lm(high_cv ~ temperature + richness_med:temperature + DBO + lat + insecticides + herbicides + insecticides, hab_press_div)
car::vif(mod)

mod <- lm(mid_cv ~ richness_med + DBO + lat + temperature + insecticides + herbicides + insecticides, hab_press_div)
car::vif(mod)
```

@@

```{r cv-sp-bm-grp3, eval = FALSE, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the high trophic group versus the biomass of the different trophic groups"}
cv_sp_grp %>%
  filter(species %in% sp_grp3$sp_class[1:10]) %>%
  ggplot(aes(x = bm_st, y = cv)) +
  geom_point() +
  facet_grid(cols = vars(troph_group), rows = vars(species), labeller = labeller(troph_group = troph_group_labeller()),
    scales = "free_x") +
  labs(x = "Biomass of the trophic group (g)", y = "CV of the species")

@@

#### Temporal dynamics in high diversity community

```{r}
high_div_station <- temporal_community_metrics %>%
  arrange(desc(richness_med)) %>%
  slice(1: 5) %>%
  select(station) %>%
  unlist
```

```{r tmp-richest, fig.dim = c(10, 7), fig.cap = "The five highest rich community."}
label_stab <- filter(temporal_community_metrics,
  station %in% high_div_station) %>%
mutate(
  x_pos = ymd_hms("2005-01-01T15:00:00"),
  x_pos = as.Date(x_pos),
  y_pos = 50000,
  text = paste0("Stability: ", round(biomass_stab,2)),
)
ggplot(filter(community_metrics, station %in% high_div_station),
  aes(y = biomass, x = date)) +
  geom_line() +
  geom_point() +
  geom_text(data = label_stab, aes(x = x_pos, y = y_pos, label =
      text), size = 6) +
  facet_wrap( ~ station) + 
  labs(y = "Biomass (g)", x = "Date")
```

```{r}
myload(network_analysis, network_metrics, dir = dest_dir)
high_div_troph_group <- network_metrics %>%
  select(opcod, troph_group) %>%
  unnest() %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  left_join(select(op_analysis, opcod, station, date)) %>%
  filter(station %in% high_div_station)
```

```{r, fig.dim = c(10, 7)}
ggplot(high_div_troph_group,
  aes(y = nbnode, x = date, color = troph_group)) +
  geom_line() +
  geom_point() +
  geom_text(data = label_stab,
    x = ymd_hms("2015-01-01T15:00:00"),
    y = 3, aes(label =
      text), size = 6, inherit.aes = FALSE) +
  facet_wrap( ~ station) + 
  labs(title = "The five richest station",
  y = "Fish species richness", x = "Date")
```

```{r}
highest_div_grp_3_station <- temporal_network_metrics_classes %>%
  select(station, troph_group) %>%
  unnest(troph_group) %>%
  filter(troph_group == 3) %>%
  arrange(desc(richness_avg)) %>%
  slice(1:12) %>%
  select(station) %>%
  unlist()
high_div_troph_group_3 <- network_metrics %>%
  select(opcod, troph_group) %>%
  unnest() %>%
  mutate(troph_group = as.factor(troph_group)) %>%
  left_join(select(op_analysis, opcod, station, date)) %>%
  filter(station %in% highest_div_grp_3_station)
```

```{r, fig.dim = c(10, 7)}
ggplot(high_div_troph_group_3,
  aes(y = biomass, x = date, color = troph_group)) +
  geom_line() +
  geom_point() +
  geom_text(data = filter(temporal_community_metrics, station %in% highest_div_grp_3_station),
    x = ymd_hms("2015-01-01T15:00:00"),
    y = 3, aes(label = paste0("Stability: ", round(biomass_stab, 2))),
    size = 6, inherit.aes = FALSE) +
  facet_wrap( ~ station) + 
  labs(title = "The twelve richest station of superior predator",
  y = "Biomass of trophic group (g)", x = "Date")
```

```{r}
ggplot(high_div_troph_group_3,
  aes(y = biomass, x = date, color = troph_group)) +
  geom_line() +
  geom_point() +
  geom_text(data = filter(temporal_community_metrics, station %in% highest_div_grp_3_station),
    x = ymd_hms("2015-01-01T15:00:00"),
    y = 3, aes(label = paste0("Stability: ", round(biomass_stab, 2))),
    size = 6, inherit.aes = FALSE) +
  facet_wrap( ~ station) + 
  labs(title = "The twelve richest station of superior predator",
  y = "Biomass of trophic group (g)", x = "Date")
```

@@

```{r colin_prod, fig.cap = "Colinearity check for total biomass"}
car::vif(lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + evt_med1 + evt_med2 + evt_cv1 + evt_cv2, random = ~ 1 | basin, data = sem_data)) %>%
  enframe %>%
  kable
```

>>>>

```{r, fig.dim = c(10, 7), include = FALSE}
synchrony %>%
  left_join(select(temporal_community_metrics, station), by =
    "station") %>%
  gather(comp, stab, synchrony:cv_com) %>%
  ggplot(aes(x = richness_med, y = stab)) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "Species diversity", y = "Stability component") +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  facet_grid(rows = vars(comp), scales = "free_y")
```

@@

### Separate core and peripherical species

#### Species peripherical globally

```{r}
myload(occurence_sp_st, dir = mypath("report"))
myload(community_analysis, dir = data_common)

global_med_occ <- occurence_sp_st %>%
  dplyr::summarise_if(is.double, list(~median(., na.rm = TRUE))) %>%
  gather(sp, med_occ, everything())

Removing the peripherical species nor at the global scale neither at the station
scale do not affect the stability-diversity relationship.

```{r stab-sp-occ, fig.dim = c(10, 7), fig.cap = "Relationship between biomass stability and species richness without peripherical species."}

threshold_occ <- c(0, .10, .30, .60, .90)
com_wo_per  <- map(threshold_occ, 
  ~rm_sp_from_com(com = community_analysis, sp_to_rm =
    global_med_occ[global_med_occ$med_occ < .x,]$sp))
names(com_wo_per) <- threshold_occ

res_sync_per <- map2_dfr(com_wo_per, names(com_wo_per), function (.data, .names) {

  sync <- compute_com_synchrony(
    .op = op_analysis,
    com = .data)
  sync$type <- .names 
  sync$biomass_stab <- 1 / sync$cv_com
  return(sync)

})

p_sync_global_per <- res_sync_per %>%
  ggplot(aes(x = richness_med, y = biomass_stab)) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  facet_grid(cols = vars(type))

p_sync_global_per
```

```{r, fig.show = "hide"}
res_sync_per %>%
  select(richness_med, biomass_stab, synchrony, cv_sp, type) %>%
  gather(stab, value, biomass_stab, synchrony, cv_sp) %>%
  ggplot(aes(x = richness_med, y = value)) +
  geom_point() +
  geom_smooth(method = "auto") +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  facet_grid(cols = vars(type), rows = vars(stab), scales = "free_y")

#### Species peripherical by station

```{r stab-occ-st, fig.dim = c(10, 7), fig.cap = "Relationship between biomass stability and species richness without peripherical species."}

res_sync_occ_st <- map_dfr(c(threshold_occ, .99), function (.threshold) {
  # List of sp to rm
  sp_to_rm <- occurence_sp_st %>%
    gather(sp, occ, -station) %>%
    group_by(station) %>%
    filter(occ < .threshold) %>%
    summarise(sp2 = list(unique(sp)))

  # Rm species by station
  truncated_com <- community_analysis %>%
    left_join(select(op_analysis, opcod, station), by = "opcod") %>%
    filter(!is.na(station)) %>%
    group_by(station) %>%
    nest() %>%
    left_join(sp_to_rm, by = "station") %>%
    mutate(
      output = map2(data, sp2, function (.data, sp_vec) {
	rm_sp_from_com(com = .data, sp_to_rm = sp_vec)
  })
      ) %>%
  unnest(output) %>%
  select(-station)

  sync <- compute_com_synchrony(
    .op = op_analysis,
    com = truncated_com)

  sync$type <- .threshold 
  sync$biomass_stab <- 1 / sync$cv_com

  return(sync)
    })

p_sync_local_per <-  res_sync_occ_st %>%
  select(richness_tot, richness_med, biomass_stab, type) %>%
  gather(rich_type, richness, richness_med, richness_tot) %>%
  ggplot(aes(x = richness, y = biomass_stab)) +
  geom_point() +
  geom_smooth(method = "lm") +
  stat_poly_eq(
    formula = y ~ x,
    eq.with.lhs = "italic(hat(y))~`=`~",
    aes(label = paste(..eq.label.., ..rr.label.., sep = "*plain(\",\")~")),
    parse = TRUE) +
  geom_smooth(method = "lm", formula = y ~ x) +
  facet_grid(cols = vars(type), rows = vars(rich_type))
p_sync_local_per
```

The removal of peripheral species does not change the relationship between stability and species richness meaning that this relation is due to species present most of the time.

@@

```{r}
library(ade4)
library(factoextra)
myload(habitat_pressure, pca_pressure, dir = mypath("report"))
```

@@

hab_press_div <- left_join(habitat_pressure,
  temporal_community_metrics[, c("station", "richness_med", "biomass_avg","biomass_stab")],
  by = "station") %>%
left_join(div_troph_grp, by = "station")
pca_hab <- dudi.pca(as.data.frame(select(pca_pressure, -station)), scannf = FALSE, nf = 5, center = TRUE, scale = TRUE)

supp_var <- pca_pressure %>%
  select(station) %>%
  left_join(select(temporal_community_metrics, station, biomass_stab,
      richness_med), by = "station")
#check
stopifnot(all(pca_pressure$station == supp_var$station))

pca_stab <- fviz_pca_biplot(
  pca_hab, geom = "point",
  col.ind = (supp_var$biomass_stab),
  pointsize = 2,
  gradient.cols = "RdYlBu",
) %>% 
ggpubr::ggpar(title = "Biomass stability")

pca_rich <- fviz_pca_biplot(
  pca_hab, geom = "point",
  col.ind = supp_var$richness_med,
  gradient.cols = "RdYlBu",
  pointsize = 2,
) %>% 
ggpubr::ggpar(title = "Species richness")
plot_grid(pca_stab, pca_rich)
```

@@

```{r cv-sp-bm-grp3, eval = FALSE, fig.dim = c(7, 21), fig.cap = "CV of the most abundant species in the high trophic group versus the biomass of the different trophic groups"}
cv_sp_grp %>%
  filter(species %in% sp_grp3$sp_class[1:10]) %>%
  ggplot(aes(x = bm_st, y = cv)) +
  geom_point() +
  facet_grid(cols = vars(troph_group), rows = vars(species), labeller = labeller(troph_group = troph_group_labeller()),
    scales = "free_x") +
  labs(x = "Biomass of the trophic group (g)", y = "CV of the species")
```

@@

@@

```{r colin_prod, fig.cap = "Colinearity check for total biomass"}
car::vif(lme(prod ~ log_rich + piel + c_c + t_lvl + beta_bin_c + RC1 + RC2 + RC3 + RC4 + RC5, random = ~ 1 | basin, data = sem_data)) %>%
  enframe %>%
  kable
```
